Modeling browser-based distributed evolutionary computation systems

### 2015-02-08 modeling-volunteer-computing-gecco.tex
Explaining the experiment

The fact that it run correctly during a massive lightning talk means that this setup is a
valid, no-cost, platform for massive evolutionary algorithms. There
were several ways of introducing it: during a talk, telling the
audience to visit the web that was posted in the first slide, and
after the talk, inserting the URL in a tweet with a brief explanation
and several tweets more indicating what it was about and what it
did. If any question arose, it was answered as fast as possible.

>>>>

The fact that it run correctly during a massive lightning talk means that this setup is a
valid, no-cost, platform for massive evolutionary algorithms. There
were several ways of introducing it: during a talk, telling the
audience to visit the web that was posted in the first slide, and
after the talk, inserting the URL in a tweet with a brief explanation
and several tweets more indicating what it was about and what it
did. If any question arose, it was answered as fast as possible. In
the first experiment, the median number of different IPs was 18, with
a maximum of 28 and a minimum of 6. In the second, the median was 12.5
with a maximum of 19 and minimum of 8. The histogram of different IPs
in each experiment is shown in figure \ref{fig:histo:ips}. Probably
the most remarkable thing is that a cluster of 6 computers can, as a
minimum, be gathered for a distributed computing experiment by just
announcing it as a tweet, but the fact that we can obtain more than a
dozen computers in more than half the cases is also remarkable, and
goes to prove the excess of computing resources that people,
willingly, lend to a simple experiment.
